---
title: "Modeling_Activity"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
```

## Step 1: Read and clean the data

```{r, message = FALSE}
churn <- read_csv(here("Data", "churn.csv"))
```

```{r}
churn <- churn %>%
  mutate(
    Geography = factor(Geography),
    Gender = factor(Gender),
    HasCrCard = factor(HasCrCard,
                       levels = c("0", "1"),
                       labels = c("No", "Yes")),
    IsActiveMember = factor(IsActiveMember,
                       levels = c("0", "1"),
                       labels = c("No", "Yes")),
    Exited = factor(Exited,
                       levels = c("0", "1"),
                       labels = c("No", "Yes")),
  ) %>%
  select(-Surname)
```



## (Old version: fit a linear model)

```{r}
my_model <- lm(Balance ~ Age, data = churn)

my_model

summary(my_model)
```

There is a significant relationship between Age and Balance. 

0.08% of the variance in Balance is explained by Age.

## Step 2:  Specify your model(s)


```{r}
lin_reg_spec <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")

lin_reg_spec

log_reg_spec <- logistic_reg() %>%
  set_mode("classification") %>%
  set_engine("glm")
```




## Step 3:  Preprocess your data

```{r}
summary(churn)

churn_rec <- recipe(Balance ~ ., data = churn) %>%
  update_role(CustomerId, RowNumber, new_role = "ID") %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_log(EstimatedSalary) %>%
  step_zv(all_predictors())

churn_rec


churn_wflow <- workflow() %>%
  add_model(lin_reg_spec) %>%
  add_recipe(churn_rec)

churn_wflow

churn_rec_log <- recipe(Exited ~ ., data = churn) %>%
  update_role(CustomerId, RowNumber, new_role = "ID") %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_log(EstimatedSalary) %>%
  step_zv(all_predictors())

churn_wflow_log <- workflow() %>%
  add_model(log_reg_spec) %>%
  add_recipe(churn_rec_log)
  
```



## Step 4:  Split into test/training sets

```{r}
set.seed(48378)

churn_split <- initial_split(churn, prop = 3/4)

churn_train <- training(churn_split)
churn_test <- testing(churn_split)
```



## Step 5:  Fit to the training set

```{r}
churn_lm_fit <- churn_wflow %>%
  fit(churn_train)

churn_lm_fit %>%
  pull_workflow_fit() %>%
  tidy()
```



## Step 6:  Predict on the test set and validate

```{r}
churn_lm_fit %>%
  predict(churn_test)

churn_test <- churn_test %>%
  mutate(
    predictions = predict(churn_lm_fit, churn_test)$.pred
  )

churn_test %>%
  bind_cols(predict(churn_lm_fit, churn_test))


churn_test %>%
  ggplot() +
  geom_point(aes(x = Balance, y = predictions))

churn_test %>%
  rsq(truth = Balance,
      estimate = predictions)
```



## Step 7:  Select your final model and fit on all the data

```{r}
churn_cv <- vfold_cv(churn, v = 5)

churn_cv_fits <- churn_wflow %>%
  fit_resamples(resamples = churn_cv)

churn_cv_fits %>%
  collect_metrics()

churn_cv_fit_log <- churn_wflow_log %>%
  fit_resamples(resamples = churn_cv)

churn_cv_fit_log %>%
  collect_metrics()
```

